---
title: "Homework1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown



How are these assumptions generated?

Write out R code for R2, RMSE, lm and coef

For questions 1 and 2, please run a linear regression 
on the data using:
```{r lm}
args(lm)
```
For output to these questions, please include 
a) a scatterplot of the dependent and indepedent variable with a line added representing best fit least squares model

b) Parameter estimates and 95% CI for slope and intercept parameters

c) A metric of model fit (either R2 or RMSE)

Question 1: 

This question refers to the following dataset:
math_scores.csv

```{r mathscores}
math<-read.csv("math_scores.csv")
head(math)
```

These data represent the average performance test scores of groups of human subjects with varying tissue concentrations of LSD (yes this is a real dataset--see citation below). Using least squares regression, calculate:

A. What level of LSD tissue concentration do you need to ensure a test score of >85%?

B. How well does LSD tissue concentration predict test performance?

C. Why might the Normal distribution be the wrong probability distribution function to model these data?

Source: Wagner, Agahajanian, and Bing (1968). Correlation of Performance Test Scores with Tissue Concentration of Lysergic Acid Diethylamide in Human Subjects. Clinical Pharmacology and Therapeutics, Vol.9 pp635-638.

Question 2:

These data refer to the data frame
miracle_food.csv

```{r math}
math<-read.csv("math_scores.csv")
head(math)
```

Data 2: poorly behaved data (high pvalue)
Interpret slope and intercept, fiit model

3: write a function for MAE. MAE is often favorable because it makes fewer assumptions about the error than R2 and RMSE. Calculate MAE, R2, and RMSE for models 1 and 2. How do they vary?

4. use rnorm to simulate a dataset with an intercept and a slope. Run a lm on this data

5. simulate and plot unequal variance of errors



1.	Write a function for mean absolute error:
Hint: here's a function for RMSE

2.	Simulate data: rnorm(..) non-linear terms
3.	Linear models: pvalues and effect sizes
4.	Compare RMSE and MAE between your different models. What can they tell you about the model?
5.	Simulate rnorm variance depends on the mean
6.	Simulate power law function (describes lots of stuff)


prediction:
```{r functions}
r2<-function(y_hat,y) {
  
  RSS<-sum((((y_hat))-(y))^2)
  
  TSS<-sum(((y)-(mean(y)))^2)
  
  return(1-RSS/TSS)}

rmse=function(y_hat,y)
{
  return(sqrt(mean((y-y_hat)^2)))
}
```

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
